---
title: "Data Wrangling Flanker Anaylsis"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message = FALSE)
```

## Flanker task


In a flanker task, participants identify a central stimulus (as quickly and accurately) as possible, while ignoring distracting stimuli presented on the left or right of the central stimulus (the flankers). 

The data for this assignment come from a flanker task where participants responded to many flanker stimuli over several trials. 

## Load the data and libraries you will use


```{r}

library(data.table)
library(dplyr)
library(ggplot2)
library(bit64)


# get the file names
file_names <- list.files(path="FlankerData")

# create headers for each column
the_headers <- c("stimulus","congruency","proportion",
                 "block","condition","dualtask","unknown",
                 "stimulus_onset","response_time","response","subject")
# Load data
# create empty dataframe
all_data<-data.frame()

# loop to add each file to the dataframe
for(i in file_names){
  one_subject <- fread(paste("FlankerData/",i, sep=""))
  names(one_subject) <- the_headers
  one_subject$subject <- rep(i,dim(one_subject)[1])
  one_subject <- cbind(one_subject, trial= 1:dim(one_subject)[1])
  all_data <- rbind(all_data,one_subject)
}

```

## Pre-processing

Create an accuracy column that codes whether the response was correct or incorrect on each trial 

```{r}
center_let<-unlist(lapply(strsplit(all_data$stimulus,""),
                         FUN=function(x)unlist(x)[2]))

all_data<-cbind(all_data,center_let)

all_data<-all_data %>%
    mutate(response=tolower(response),
    center_let=tolower(center_let),
    accuracy=response==center_let)
  

```

### Get Reaction time on each trial

 Add a column that calculates the reaction time on each trial.


```{r}

# Somehow the stimulus and the response time are the same number?

all_data <- all_data %>%
              mutate(RT = as.integer(response_time - stimulus_onset))

```


## Checks

Check how many trials each subject completed in the congruent and incongruent conditions, the mean accuracy for each subject in each congruency condition, and the mean RT for each subject in each congruency condition.

```{r}

Sub_Trials <- all_data %>%
                  mutate(subject = as.factor(subject),
                         congruency = as.factor(congruency)) %>%
                  group_by(subject,congruency) %>%
                  summarise(num_trials = length(RT),
                            mean_RT = mean(RT),
                            mean_accuracy = mean(accuracy))
knitr::kable(Sub_Trials)
```



### Exclusion

Exclude all RTs that are longer than 2000 ms

```{r}

# Reaction Time =0 somehow the stimulus and response are the same number
Slow_RT <- all_data %>%
              filter(RT < 2000)
```

## Analysis

### Reaction Time analysis

1. Get the individual subject mean reaction times for **correct** congruent and incongruent trials.

```{r}
Subject_Trials_meanRTs <- Slow_RT %>%
                    filter(accuracy == TRUE) %>%
                    group_by(subject,congruency) %>%
                    summarise(mean_RT = mean(RT))
```

2. Get the overall mean RTs and SEMs (standard errors of the mean) for the congruent and incongruent condition. Make a table and graph.

```{r}

 congruency_means <- Subject_Trials_meanRTs %>%
                      group_by(congruency) %>%
                      summarise(meanRT = mean(mean_RT),
                                SEM = sd(mean_RT)/sqrt(length(mean_RT)))
knitr::kable(congruency_means)

ggplot(congruency_means, aes(x=congruency,y=meanRT,
                             fill=congruency))+
  geom_bar(stat="identity")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time ")+
  geom_errorbar(aes(ymin=meanRT-SEM,
                    ymax=meanRT+SEM),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(100,1000))

