---
title: "Norlander Learn's R "
output: html_document
---

<style type="text/css">
.title {
  display: none;
}

#getting-started img {
  margin-right: 10px;
}

</style>
### Problem 1 

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+1 
3-2
4*6
5/7
```

#Problem 2 

Put numbers into variables, do simple math on the variables
```{r, eval=FALSE}
Norie <-1
ABC <-537848756781637

a <-1
b <-"five"

a+b
```
#Problem 3 

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.


```{r}
Numbers_List <-seq(1:100)

for (i in 1:length(Numbers_List)){
  print(Numbers_List[[i]])
}

```
#Problem 4
Find the sum of all the integer numbers from 1 to 100

```{r}
Numbers_List <-seq(1:100)

for (i in 1:length(Numbers_List)){
  print(Numbers_List[[i]])
}
sum(Numbers_List)
```

#Problem 5 
Write a function to find the sum of all integers between any two values.


#Problem 6 
List all of the odd numbers from 1 to 100.
```{r}
Odd_numbers <-seq(1, 99, 2)
 print(Odd_numbers)

```

#Problem 7 
List all of the prime numbers from 1 to 1000.
```{r}
Prime_Numbers <-(1:500)*2
print(Prime_Numbers)
```

#Problem 8 
Generate 100 random numbers
```{r}
rnorm(100) 
```

#Problem 9 
Generate 100 random numbers within a specific range 
<!-- ASK IF THESE PARMETERS ARE WHAT HE WANTS? -->
```{r}
rnorm(100, mean = 6, sd = 6)

```

#Problem 10 A Mean
Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation

```{r}
x_mean <-c(1,3,9,-22,22,6,7,10,15,4,25)
my_fun <-function(x_mean){ sum(x_mean)/length(x_mean)} 
print(my_fun(x_mean))
```


#Problem B Mode
```{r}
Y<-c(1,3,9,-22,22,6,7,10,15,4,25,22,56,7,22,22)
table(Y)
C=table(Y)

names(which.max(C))


```

#Problem 11 
Count the number of characters in a string variable. 
```{r}
Count1 <-c(1,3,9,-22,22,6,7,10,15,4,25)

length(Count1)

```

#Problem 12 
Count the number of words in a string variable
```{r}
letter<-c("jtymhrtyoilnk")
strsplit(letter, split = "")

length(letter)

```
#Problem 13 
Count the number of sentences in a string variable
```{r}
strV<-"How can we understand R if we don't read"
sapply(strsplit(strV," "),length)

```
#Problem 14 *ASK*
Count the number of times a specific character occurs in a string variable

```{r}
Str1<-"bbbjshjfsiiiisihfksbjsuuuus"
(strsplit(Str1,""))

table(Str1)


```
#Problem 15 
Do a logical test to see if one word is found within the text of another string variable.

```{r}
Word<-"Learning"
sentence<-" Learning R is hard "

grepl(Word,sentence)

```
#Problem 16 ASK
Put the current computer time in milliseconds into a variable

```{r}
print(as.numeric(Sys.time())*1000, digits=15)
```
#Problem 17

#Problem 18

#Problem 19
Output the contents of a variable to a .txt file

```{r}

```
#Problem 20  
Create a variable that stores a 20x20 matrix of random numbers

```{r}

```
#Problem 21
Output any matrix to a txt file using commas or tabs to separate column values, and new lines to separate row values

```{r}

```







