---
title: "Common inferential tests"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
##Null Distributions


###1) Sample from normal distribution/create a null
```{r}
Stat<-rnorm(10,0,1)
hist(Stat)

# More normal
hist(rnorm(1000000,0,1))


#Replicate
replicate(100,rnorm(10,0,1))
```
###2) Get the mean differences
```{r}

#get sample mean
mean(Stat)

#Use a for loop
savemeans<-c()
for(i in 1:1000){
  savemeans[i]<-mean(rnorm(10,0,1))

}

null <- replicate(10000,mean(rnorm(10,0,1)-mean(rnorm(10,0,1))))                
```
###3) Is it by chance? Alpha<.05
```{r}

Crit_val<- sort(null)
Crit_val[9500]

#nondirectional
Absolute_cv <- sort(abs(null))
Absolute_cv[9500]
```
###T test

Show that the properties of a simulated t-distribution are the same as the properties of the analytic t-distribution. Assume df = 9.

For example, what are the probabilities of t(9) >= .5, 1, 1.5, 2, and 2.5? These p-values can be obtained using the  qt() function.

Create a simulated t-distribution for the null hypothesis with df=9. Here, the model situation involves taking samples of size n=10 from a normal distribution. The t-value is computed for each sample (sample mean - 0)/SEM. The process is repeated 10,000 times, and each t-value is saved. The resulting 10,000 t-values are the simulated t-distribution.

Using the simulated t-distribution, find the probability of t(9) >= .5, 1, 1.5, 2, and 2.5

Compare the two sets of probabilities to show that the difference is small. What happens to the difference if the simulation is repeated fewer times (e.g., 100) vs. more times (e.g., 100,000)
```{r}
t_dist <- replicate(10000,t.test(rnorm(10,0,1))$statistic)

hist(t_dist)

length(t_dist[t_dist<.5])/10000
length(t_dist[t_dist<1])/10000
length(t_dist[t_dist<1.5])/10000
length(t_dist[t_dist<2])/10000
length(t_dist[t_dist<2.5])/10000


#With a loop
ts <- c(.5,1,1.5,2,2.5)
sim_t <- c()
for(i in ts){
  sim_t <- c(sim_t,length(t_dist[t_dist >= i])/10000)
}
  
sim_t-(1-pt(ts,9))
```
###Correlation
```{r}
null <- replicate(10000,cor(rnorm(10,0,1),rnorm(10,0,1)))
sorted_null <- sort(abs(null))
sorted_null[9500]
null <- replicate(10000,cor(rnorm(100,0,1),rnorm(100,0,1)))
sorted_null <- sort(abs(null))
sorted_null[9500]

run_anova<-function(){
  A<-rnorm(4,0,1)
  B<-rnorm(4,0,1)
  C<-rnorm(4,0,1)
  
  
con<-rep(c("A","B","C"),each=4)
DV<-c(A,B,C)
df<-data.frame(con,DV)
sum_out<-summary(aov(DV~con,df))
return(sum_out[[1]]$`F value`[1])

}

save_fs<-replicate(1000,run_anova())
hist(save_fs)

sort(save_fs)[9500]

qf(.95,2,9)
